---
title: "hw5"
author: "Henry Stoddard"
date: "11/10/2020"
output: github_document
---
```{r}
library(readr)
library(tidyverse)
library(ggplot2)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

Load libraries, read in data
## Problem 1
```{r}
homicide_df =
  read_csv("data/homicide-data.csv") %>% 
  mutate(
    city_state = str_c(city, state, sep = "_"),
    resolved = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest" ~ "unsolved",
      disposition == "Closed by arrest" ~ "solved",
    )
  ) %>% 
  select(city_state, resolved) %>% 
  filter(city_state != "Tulsa_AL")
```
This dataset contains information on homicide reports by city. It contains the report date,
victim's name, age, and sex, and the outcome of the case.

Looking closer, city by city

```{r}
aggregate_df =
homicide_df %>% 
  group_by(city_state) %>% 
  summarize(
    hom_total = n(),
    hom_unsolved = sum(resolved == "unsolved")
  )
```

Prop test for single city

```{r}
prop.test(
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_unsolved), aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_total)) %>% broom::tidy()
```

Now trying to iterate
We want to run that above prop.test on every row within the aggregate_df and create a new column for those results (using map2 because mapping over multiple inputs)
```{r}
results_df =
aggregate_df %>% 
  mutate(
    prop_tests = map2(.x = hom_unsolved, .y = hom_total, ~prop.test(x = .x, n = .y)),
    tidy_tests = map(.x = prop_tests, ~broom::tidy(.x))
  ) %>% 
  select(-prop_tests) %>% 
  unnest(tidy_tests) %>% 
  select(city_state, estimate, conf.low, conf.high)
```

```{r}
results_df %>%
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```

Above code creates a graph showing the proportion of unsolved homicides with 
confidence intervals by city (in ascending order).


## Question 2
Importing and tidying new dataset.
```{r}
path_df = 
  tibble(
  path = list.files("data2")) %>% 
  mutate(path = str_c("data2/", path),
         data = map(.x = path, ~read_csv(.x))) %>% 
  unnest(data) %>% 
  mutate(ID1 = str_replace(path, ".*/", ""),
         ID2 = str_replace(ID1, ".csv", "")) %>% 
  select(-ID1, -path) %>% 
  select(ID2, everything()) %>% 
  separate(ID2, c("treatment", "ID"), sep = "([_])", convert = TRUE) %>% 
  pivot_longer(week_1:week_8, names_to = "time", values_to = "score")

read_csv(path_df$path[[1]])

data_1 = read_csv("data2/con_01.csv")


```

This dataset has been tidied and now contains treatment (control or experimental),
ID #, and measurements from weeks 1-8.
Now creating a spaghetti plot showing observations on each subject over time.
```{r}
spag_plot = 
path_df %>% 
  ggplot(aes(x = time, y = score, group = ID, color = ID)) +
  geom_point() +
  geom_line() +
  facet_grid(. ~ treatment)
  
```
The control group appears to have started with lower scores and remained low.
The experimental group appears to have started with higher scores and got even
higher scores over time.

## Question 3
simulate, will use t.test and broom::tidy to export results (use sim_mean_sd and other functions in class and modify), need to get estimates and p-vals

compare t.test against mu=0 always I think

hard part is graphs, make sure to filter for where p<.05